---
title: "Project"
author: "Waruna H.R.N.A. 239183M"
date: "2023-06-30"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(ggplot2)
library(scales)
library(schoRsch)
library(xtable)
```


```{r cars}
# Importing Data
data <- read.csv('D:/MSC/SEM 2/CS5651 - Statistical Inference/Project/239183M_data_file_1.csv',header = T)
```

```{r}
# View the structure of the dataset
str(data)
```

```{r}
summary(data)
```

```{r}
data$total_expenditure <- data$average_monthly_expenditure_food.Rs. + data$average_monthly_expenditure_non_food.Rs.
```


```{r}
# histogram of average_monthly_expenditure_food.Rs.
ggplot(data, aes(x=average_monthly_expenditure_food.Rs.)) +
  theme_classic()+
  labs(
    title = "Histogram of Average Monthly Expenditure For Food In Rupees\n (sample distribution)",
    x = "",
    y = "Frequency"
  )+
  geom_histogram(binwidth = 10000, boundary = 0, closed = "left",fill = "blue", color = "black", xlab = '') +
  scale_x_continuous(breaks = seq(0, 100000, 10000),labels = comma_format())+
  theme(plot.title = element_text(hjust = 0.5))
  

```


```{r}
food <- data[,"average_monthly_expenditure_food.Rs."]

sample_size <- 50
no_of_samples <- 10000

food_distri_means <- c()

for(i in 1:no_of_samples){
  sample1 <- sample(food,50,replace=T)
  food_distri_means[i] <- mean(sample1)
}

```


```{r}
hist(food_distri_means,main = "Histogram of average Monthly expenditure for food.Rs. \n (Bootstrap Distribution)",col = "aquamarine",xlab = '')
```

```{r}
paste("Food sample mean:",mean(data$average_monthly_expenditure_food.Rs.))
```



# H0: Mean of the food expenditure distribution = 22,130
# H1: Mean of the food expenditure distribution != 22,130
```{r}
z_test_statistic <- (22130 - mean(data$average_monthly_expenditure_food.Rs.))/(sd(food_distri_means))
```

```{r}
z_test_statistic
```
```{r}
pnorm(z_test_statistic,0,1,lower.tail = T)
```
Since P value is less than 0.05 we do reject Null hypothesis




```{r}
ggplot(data, aes(x=average_monthly_expenditure_non_food.Rs.)) +
  theme_classic()+
  labs(
    title = "Histogram of Average Monthly Expenditure For non-food In Rupees\n (sample distribution)",
    x = "",
    y = "Frequency"
  )+
  ggtitle("Histogram of Average Monthly Expenditure \n For non-food In Rupees")+
  geom_histogram(binwidth = 10000, boundary = 0, closed = "left",fill = "coral1", color = "black") +
  scale_x_continuous(breaks = seq(0, 150000, 10000),labels = comma_format()) +
  theme(axis.text.x = element_text(angle = 20),plot.title = element_text(hjust = 0.5))
```



```{r}
non_food <- data[,"average_monthly_expenditure_non_food.Rs."]

sample_size <- 50
no_of_samples <- 10000

non_food_distri_means <- c()

for(i in 1:no_of_samples){
  sample1 <- sample(non_food,50,replace=T)
  non_food_distri_means[i] <- mean(sample1)
}
```



```{r}
hist(non_food_distri_means,main = "Histogram of average Monthly expenditure for Non food.Rs. \n (Bootstrap Distribution)",col = "bisque1",xlab = "")
```

```{r}
mean(mean(data$average_monthly_expenditure_non_food.Rs.))
```


# H0: Mean of the food expenditure distribution = 41,000
# H1: Mean of the food expenditure distribution != 41,000
```{r}
z_test_statistic_non_food <- (41000 - mean(data$average_monthly_expenditure_non_food.Rs.))/(sd(non_food_distri_means))
```

```{r}
z_test_statistic_non_food
```

```{r}
pnorm(z_test_statistic_non_food,0,1,lower.tail = T)
```
Since P value is greater than 0.05 we do not reject Null hypothesis



```{r}
# Perform independent two-sample t-test
result <- t.test(data$average_monthly_expenditure_food.Rs., data$average_monthly_expenditure_non_food.Rs.)
result
```

```{r}
# Create a data frame for the table
table_data <- data.frame(
  "Statistic" = c("t-value", "df", "p-value", "95% CI"),
  "Value" = c(result$statistic, result$parameter, result$p.value, paste("(", result$conf.int[1], ",", result$conf.int[2], ")"))
)

# Convert the data frame to an xtable object
table_x <- xtable(table_data)

# Print the xtable object in LaTeX format
print(table_x, type = "latex")
```




### House Architecture and related information

```{r}
# House Built Period
library(RColorBrewer)
myPalette <- brewer.pal(5, "Set2") 

pie(table(data$house_built_period),col=myPalette)
```

```{r}
ggplot(data, aes(x=house_type)) +
  ggtitle("Barplot of House Type") +
  geom_bar(fill = "green", color = "black")+
  theme(axis.text.x = element_text(size = 8),plot.title = element_text(hjust = 0.5))
```


```{r}
data["ironing_clothes_behavior"][data["ironing_clothes_behavior"] == "We don’t iron cloths."] <- "don’t iron"
data["ironing_clothes_behavior"][data["ironing_clothes_behavior"] == "We iron our clothes twice a week."] <- "twice a week"
data["ironing_clothes_behavior"][data["ironing_clothes_behavior"] == "We iron the clothes weekly."] <- "weekly"
data["ironing_clothes_behavior"][data["ironing_clothes_behavior"] == "We iron the cloths daily."] <- "daily"
data["ironing_clothes_behavior"][data["ironing_clothes_behavior"] == "We iron when and where the need arises."] <- "need arises"


```



```{r}
ironing_clothes <- data[,"ironing_clothes_behavior"]
table(ironing_clothes)
```

```{r}
data["night_lighting_behavior"][data["night_lighting_behavior"] == "We don’t keep any of the lights on when sleeping."] <- "don’t keep any"
data["night_lighting_behavior"][data["night_lighting_behavior"] == "We keep less than two-night lights on when sleeping"] <- "less than two"
data["night_lighting_behavior"][data["night_lighting_behavior"] == "We keep more than two lights on when sleeping"] <- "more than two"
```


```{r}
night_lighting <- data[,"night_lighting_behavior"]
table(night_lighting)
```

```{r}
ironing_clothes_night_lighting <-table(ironing_clothes,night_lighting)
ironing_clothes_night_lighting
```

```{r}
# Convert the data frame to an xtable object
table_x <- xtable(ironing_clothes_night_lighting)

# Print the xtable object in LaTeX format
print(table_x, type = "latex")
```

# H0:night lighting not associated with ironing clothes
# H1:night lighting associated with ironing clothes
```{r}
chisq.test(ironing_clothes, night_lighting, correct=FALSE)
```


```{r}
library(RColorBrewer)
myPalette <- brewer.pal(5, "Set2") 

pie(table(data$main_occupation),col=myPalette)
```


```{r}
library(RColorBrewer)
myPalette <- brewer.pal(5, "Set2") 

pie(table(data$major_type_of_roof_installation),col=myPalette)
```

```{r}
library(RColorBrewer)
myPalette <- brewer.pal(5, "Set2") 

pie(table(data$outside_walls_material),col=myPalette)
```



```{r}
library(RColorBrewer)
myPalette <- brewer.pal(5, "Set2") 

pie(table(data$energy_rating_of_appliance_check),col=myPalette,main = "Energy rating appliance check")
```

```{r}
table(data$energy_rating_of_appliance_check,data$electricity_meter_overconsumption)
```

```{r}
chisq.test(data$energy_rating_of_appliance_check,data$electricity_meter_overconsumption, correct=FALSE)
```



```{r}
#data$wiring_done_by_a_professional_electrician
data_new <- filter(data, wiring_done_by_a_professional_electrician == 'Yes' | wiring_done_by_a_professional_electrician == 'No')
```

```{r}
table(data_new$house_built_period, data_new$wiring_done_by_a_professional_electrician)

```

```{r}
chisq.test(data_new$house_built_period,data_new$wiring_done_by_a_professional_electrician, correct=FALSE)
```


